formula1

### 2020-06-18 inst/f1points.Rmd
more work

@@

Here we follow the above protocol to assess different plausible points
systems.  There are a number of plausible points systems that might be
used:

\begin{itemize}
\item winner takes all $(1,0,0,\ldots)$
\item Zipfs law $(1,1/2,1/3,1/4,\ldots)$
\item exponential decay $(1,r,r^2,r^3,\ldots)$
\item the actual real one $(25,18,15,12,10,8,6,4,2,1)$
\item equal points to the top $n$ competitors $\underbrace{1,1,\ldots
,1}_{n},0,0,\ldots$ (noting that $n=1$ corresponds to winner takes all)
\item linear decrease $(n,n-1,n-2,\ldots,3,2,1,0)$
\end{itemize}

@@

```{r,label=multiplemontecarlotabulation,echo=FALSE}
M3 <- t(apply(OO,1,function(o){tabulate(o+1,nbins=12)}))
dimnames(M3) <- list(system=names(pointslist),correct=0:11)
M3
Mc <- t(apply(M3,1,cumsum))
Mc
```

>>>>

Here we follow the above protocol to assess different points systems.
There are a number of plausible points systems that might be used:

\begin{itemize}
\item Exponential decay $(1,r,r^2,r^3,\ldots)$ for some fixed $r<1$
\item Equal points to the top $n$ competitors
$(\underbrace{1,1,\ldots ,1}_{n},0,0,\ldots)$, noting that
$n=1$ corresponds to a ``winner takes all''
\item Linear decrease $(r,r-1,r-2,\ldots,3,2,1,0)$ for integer $0<r<n$
\item Zipf's law $(1,1/2,1/3,1/4,\ldots)$
\item The current Formula 1 system $(25,18,15,12,10,8,6,4,2,1)$
\end{itemize}

Applying Zipf's law, for example, to the 2017 table we would rank the
drivers as follows:

```{r,label=zipfpointsshower,echo=FALSE}
zipf <- ordertable2points(ranktable_to_ordertable(wikitable_to_ranktable(F1_table_2017)),1/seq_len(top))
zipf <- round(zipf[seq_len(top)],2)
zipf <- sort(zipf,decreasing=TRUE)
zipf[] <- seq_along(zipf)
zipf
```

compare the real:

```{r,label=realpointsshower,echo=FALSE}
real <- ordertable2points(ranktable_to_ordertable(wikitable_to_ranktable(F1_table_2017)),p)
real <- round(real[seq_len(top)],2)
real <- sort(real,decreasing=TRUE)
real[] <- seq_along(real)
real
```

Thus these two systems agree on the first three places but fourth is
awarded to Ricciardo and Raikkonen respectively.

@@

We now assess the various points systems discussed above, using 1000
_in silico_ trials:

@@

```{r,label=multiplemontecarlotabulation,echo=FALSE}
M3 <- t(apply(OO,1,function(o){tabulate(o+1,nbins=12)}))
dimnames(M3) <- list(system=names(pointslist),correct=0:11)
M3
Mc <- t(apply(M3,1,cumsum))
Mc
Md <- t(apply(M3[,-1],1,cumsum))
colnames(Md) <- paste("<=",colnames(Md),sep="")
Md
```
